Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches

### 2021-04-20 paper.tex
kamer

Sketch-based IM methods are cheaper compared to simulation-based methods. They usually pre-compute the sketches by processing the graph for evaluating the influence spread instead of running simulations repetitively. One of the popular methods for sketch-based influence maximization is {\sc Skim}~\cite{cohen2014sketch} by Cohen~et~al. {\sc Skim} is a parallel algorithm which uses combined bottom-$k$ min-hash reachability sketches~\cite{bottomk,cohen2015all} with $k = 64$, and $\ell$ sampled subgraphs, to estimate the influence scores of the seed sets~\cite{cohen2014sketch}. In this work, we preferred Flajolet-Martin~\cite{flajolet1985probabilistic} instead of bottom-$k$ min-hash sketches for simplicity, suitability for vectorization and fused sampling, and hence, execution-time performance.

>>>>

Sketch-based IM methods are cheaper compared to simulation-based methods. They usually pre-compute the sketches by processing the graph for evaluating the influence spread instead of running simulations repetitively. One of the popular methods for sketch-based influence maximization is {\sc Skim}~\cite{cohen2014sketch} by Cohen~et~al. {\sc Skim} is a parallel algorithm which uses combined bottom-$k$ min-hash reachability sketches~\cite{bottomk,cohen2015all} with $k = 64$, and $\ell$ sampled subgraphs, to estimate the influence scores of the seed sets~\cite{cohen2014sketch}. In this work, we preferred Flajolet-Martin~\cite{flajolet1985probabilistic} sketches instead for their simplicity, suitability for vectorization and fused sampling, and hence, execution-time performance.
